GNSS-based displacement detection using Bayesian inference for deformation monitoring

### 2020-11-22 paper/manuscript-iot.tex
modify introduction

	\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
	Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields. 
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\cite{shen2019a}. 
	Displacement detection involves automatic identification of the time of displacement and determination of displacement. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. There are many researches on displacement detection based on GNSS, which can be divided into two categories.

>>>>

	\section{Introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to natural disaster monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields. 
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
	With the improvement of the Internet of things (IOT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time.
	%Displacement detection involves displacement identification and extraction. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. 
	There are many researches on displacement detection based on GNSS, which can be divided into two categories.
